---
title: "ggplot2-notes"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Kara"
date: "2020/1/25"
output: html_document
---

&emsp;  
**<font color="red">Import, tidy, transform, visualize and model data.</font>**  

# 1. Explore  
<font color = "black">_Data exploration is the art of looking at your data, rapidly **generating hypotheses**, quickly **testing** them, then repeating again and again and again._  

## Chap.1 ggplot2 visualization
**<font color = "red">Question:** <font color = "black">do cars with big engines use more fuel than cars with small engines?  

```{r}
library(tidyverse)

ggplot(mpg) + 
  geom_point(aes(displ, hwy), color = "#00AFBB") +
  xlab("Engine Size") +
  ylab("Fuel Efficiency") +
  theme_bw()
```
```{r}
# add a third variable like class  
ggplot(mpg) + 
  geom_point(aes(displ, hwy, color = class)) +
  xlab("Engine Size") +
  ylab("Fuel Efficiency") +
  theme_bw()
```
Sports cars have large engines like SUVs and pickup trucks, but small bodies like midsize and compact cars, which improves their gas mileage.  

### Facets  

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  facet_wrap(~ class, nrow = 2) +
  xlab("Engine Size") +
  ylab("Fuel Efficiency") +
  theme_bw()
```
```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  facet_grid(drv ~ cyl) + #两个变量分组
  theme_bw()
```
```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  facet_grid(.~ cyl) +  # 单变量同行展示
  theme_bw()
```
```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  facet_grid(drv ~.) +  # 单变量分组同列
  theme_bw()
```
### Geometric Object  

```{r}
ggplot(mpg) +
  geom_smooth(aes(displ, hwy,
                  color = drv), # 注意color在aes里面赋值
              method = "loess")
```
Here geom_smooth() separates the cars into three lines based on their drv value, which describes a car’s drivetrain.  
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point() +
  geom_smooth(method = "loess")
# If you place mappings in a geom function, ggplot2 will treat them as local mappings for the layer.
```
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(aes(color = class)) + 
  geom_smooth(method = "loess")
```
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(data = filter(mpg, class == "subcompact"), 
              method = "loess",
              se = FALSE)
```
### Exercise  
```{r}
p0 <- ggplot(mpg, aes(displ, hwy)) +
  geom_point()
p1 <- p0 + geom_smooth(color = "blue",
              method = "loess",
              se = FALSE)
p2 <- p0 + geom_smooth(aes(group = drv),
                       method = "loess",
              se = FALSE)
library(gridExtra)
grid.arrange(p1,p2,nrow=1) # 同行展示
```
```{r}
p0_1 <- ggplot(mpg, aes(displ, hwy)) + 
  geom_point(aes(color = drv))

p3 <- p0_1 +
  geom_smooth(aes(group = drv, color = drv),
              method = "loess",
              se = FALSE)

p4 <- p0_1 +
  geom_smooth(method = "loess",
              se = FALSE)

p5 <- p0_1 + 
  geom_smooth(aes(linetype = drv),
              method = "loess",
              se = FALSE)

p6 <- ggplot(mpg, aes(displ, hwy)) +
  geom_point(color = "white",
             size = 5) +
  geom_point(aes(color = drv),
             size = 2)

grid.arrange(p3,p4,p5,p6,nrow=2)
```